KidsAIR: exposure model

### 2020-04-28 exposure_models.Rmd
exposure analysis updates

####### Format home activity data to merge with analysis data below
home_activity_data <- exposure_analysis_data_medium %>% 
  filter(treatment == "Placebo") %>% 
  #filter(winter_id == 1) %>% 
  select(home, area, home_winter_id, sampling_day, starts_with("home_act")) %>% 
  group_by(area, home, home_winter_id) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  group_by(area, home, home_winter_id) %>% 
  mutate_at(vars(starts_with("home_act")), as.numeric) %>% 
  mutate_at(vars(starts_with("home_act")), funs(. - 1)) %>% 
  mutate_at(vars(starts_with("home_act")), funs(sum(.))) %>% 
  ungroup() %>% 
  distinct(area, home,  home_winter_id, .keep_all = TRUE)

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  group_by(home) %>% 
  mutate(residents_smoke = if_else(winter_id == 1 & is.na(residents_smoke),
                                   lead(residents_smoke), residents_smoke)) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home", "home_winter_id")) %>% 
  select(pm_mean_sampling_period, area, income_3level, 
                 stove_age_3level, home_windows_2level,
                 chimney_clean_3level, wood_collect_2level, 
                 home_act_door, home_act_smoking, home_act_sweep, home_act_windows, 
                 stove_grade_3level, moisture_closest_2level,
                 total_residents_2level, mean_temp_sampling_period_5) %>% 
  filter(!is.na(pm_mean_sampling_period))

@@

>>>>

####### Format home activity data to merge with analysis data below
home_activity_data <- exposure_analysis_data_medium %>% 
  filter(treatment == "Placebo") %>% 
  #filter(winter_id == 1) %>% 
  select(home, area, home_winter_id, sampling_day, starts_with("home_act")) %>% 
  group_by(area, home, home_winter_id) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  group_by(area, home, home_winter_id) %>% 
  mutate_at(vars(starts_with("home_act")), as.numeric) %>% 
  mutate_at(vars(starts_with("home_act")), funs(. - 1)) %>% 
  mutate_at(vars(starts_with("home_act")), funs(sum(.))) %>% 
  mutate_at(vars(starts_with("home_act")), factor) %>%
  ungroup() %>% 
  distinct(area, home,  home_winter_id, .keep_all = TRUE)

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  #filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  group_by(home) %>% 
  mutate(residents_smoke = if_else(winter_id == 1 & is.na(residents_smoke),
                                   lead(residents_smoke), residents_smoke)) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home", "home_winter_id")) %>% 
  replace_with_na(replace = list(mean_temp_sampling_period_5 = "NaN")) 
```

@@

Looking at model selection and averaging after multiple imputation

Helpful manuals and vignettes:

https://cran.r-project.org/web/packages/mice/mice.pdf

```{r}
library(mice)

# Select analysis vars
selected_vars <- analysis_data %>% 
  select(area, pm_mean_sampling_period, income_3level, residents_smoke, 
         stove_age_3level, home_windows_2level,
         chimney_clean_3level, wood_collect_2level,
         home_act_door, home_act_sweep, home_act_windows, 
         sums_events_sampling_period, mean_temp_sampling_period_5, 
         stove_grade_3level, moisture_closest_2level) %>% 
  mutate(home_act_door = factor(home_act_door, levels = c(0,1,2,3,4,5,6)),
         home_act_sweep = factor(home_act_sweep, levels = c(0,1,2,3,4,5,6)),
         home_act_windows = factor(home_act_windows, levels = c(0,1,2,3,4,5,6)),
         area = factor(area, levels = c("AK", "NN", "WMT")))

# Check % missing data
mean(is.na(selected_vars))

# Using mice package

# Look for patterns in missing data
md.pattern(selected_vars)

# Impute missing data; m = 20 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=5,
                     method = c("polyreg", "pmm", "polr", "logreg", "polr",
                                "logreg", "polr", "logreg", "polr", "polr",
                                "polr", "pmm", "pmm", "polr", "logreg"))

summary(imputed_data)

# Can add "long" or "broad arguments
complete(imputed_data, "long")

# Sample one of the imputed datasets
check1 <- complete(imputed_data, 3)

densityplot(selected_vars$pm_mean_sampling_period)

# Use seed to get the exact same results from random sampling
# seed = 123

# See vignette #2 for setting up predictor matrices and relationships b/w vars

# Check for convergence
## In general, we would like the streams to intermingle and be free of any trends 
## at the later iterations.
plot(imputed_data)

# Check that the imputation method matches the data type correctly
## particularly for PM that should be log transformed, and the factors

stripplot(imputed_data)

# Can do regression on the imputed data - either pooled or individual datasets

```

http://mami.r-forge.r-project.org/MAMI_manual.pdf

```{r}
library(MAMI)

# Using MAMI package, perform model averaging and selection
model_ave <- mami(imputed_data, missing.data = "imputed", model = "gaussian",
                  outcome = "pm_mean_sampling_period", 
                  method = "MA.criterion", criterion = "AIC", print.time = TRUE,
                  add.transformation = c("log(pm_mean_sampling_period)"))

                  #inference = "+boot", B = 2, X.org = selected_vars

summary(model_ave)
plot(model_ave)
```
